**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2017-05-29 doc/adaAbstract.Rmd
removed gee graph that is non-functional

# Boxplot of ACR in uVDBP categories
dsBase %>% 
  select(UDBPStatus, ACR) %>% 
  na.omit() %>% 
  box_plot("UDBPStatus", "log(ACR)",
           "Urinary VDBP status",
           "log Urine ACR (mg/mmol)")

@@

```{r hyperfiltration}
ds %>% 
  dplyr::filter(eGFR < 45) %>% 
  dplyr::select(SID, VN, Age, eGFR, dm_status, acr_status)

@@

gee %>% 
  dplyr::mutate(Xterms = term) %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(Yterms = factor(Yterms, 
                                levels = c("ACR", "eGFR"),
                                ordered = TRUE),
                Xterms = factor(Xterms,
                                levels = rev(c("<-Xterm",
                                           "VN",
                                           "ageBase",
                                           "SexMale",
                                           "EthnicityEuropean",
                                           "BMI",
                                           "fDMdiabetes")),
                                labels = rev(c("uVDBP",
                                           "Follow-up Duration",
                                           "Baseline Age",
                                           "Sex (male)",
                                           "Ethnicity (European)",
                                           "BMI",
                                           "Diabetes")),
                                ordered = TRUE)) %>% 
  arrange(Xterms) %>% 
  gee_plot(xlab = "Unit change for every unit increase in uVDBP")
```

Graph
```{r gee plot}

gee %>%
  dplyr::mutate(p.value = ifelse(p.value > 0.05, 1, 0.04)) %>%
  seer::view_main_effect(
  graph.options = 'dot.size',
  groups = '~Yterms',
  legend.title = 'p-values',
  xlab = 'Percent difference with 95% CI in the outcomes\nfor each unit increase in baseline uVDBP',
  ylab = 'Kidney Measures'
  ) +
  graph_theme(ticks = FALSE, legend.pos = 'right') +
  ggplot2::theme(legend.margin = grid::unit(0, 'cm'))

>>>>

@@

```{r hyperfiltration}

ds %>% 
  dplyr::filter(eGFR < 45) %>% 
  dplyr::select(SID, VN, Age, eGFR, dm_status, acr_status)

@@

gee %>% 
  dplyr::mutate(Xterms = term) %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(Yterms = factor(Yterms, 
                                levels = c("ACR", "eGFR"),
                                ordered = TRUE),
                Xterms = factor(Xterms,
                                levels = rev(c("<-Xterm",
                                           "VN",
                                           "ageBase",
                                           "SexMale",
                                           "EthnicityEuropean",
                                           "BMI",
                                           "fDMdiabetes")),
                                labels = rev(c("uVDBP",
                                           "Follow-up Duration",
                                           "Baseline Age",
                                           "Sex (male)",
                                           "Ethnicity (European)",
                                           "BMI",
                                           "Diabetes")),
                                ordered = TRUE)) %>% 
  arrange(Xterms) %>% 
  gee_plot(xlab = "Percent difference in outcome for every unit increase in uVDBP")
```
